---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DNA Methylation Arrays Processing And Quality-Control

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![GitHub tag](https://img.shields.io/github/tag/umr1283/dmapaq.svg?label=latest tag&include_prereleases)](https://github.com/umr1283/dmapaq)
[![R build status](https://github.com/umr1283/dmapaq/workflows/R-CMD-check/badge.svg)](https://github.com/umr1283/dmapaq/actions)
<!-- badges: end -->

## Installation

```{r, eval = FALSE}
# Install dmapaq from CRAN:
install.packages("dmapaq")

# Or the the development version from GitHub:
# install.packages("remotes")
remotes::install_github("umr1283/dmapaq")
```

## Overview 

* `read_idats()` allows to efficiently import idats files mostly 
    using [minfi](https://bioconductor.org/packages/minfi/) functions.
* `qc_idats()` allows to compute quality-control of methylation array from Illumina 
    using a [rmarkdown template](inst/rmarkdown/templates/qc_idats/skeleton/skeleton.Rmd).

---

## Getting help

If you encounter a clear bug, please file a minimal reproducible example on [github](https://github.com/umr1283/dgapaq/issues).  
For questions and other discussion, please contact the package maintainer.

## Code of Conduct

Please note that the `dgapaq` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
